Differential geometric algebra with Leibniz and Grassmann

### 2019-10-31 paper/paper.tex
improved vectorfield and finalized JuliaCon paper, fixed #37

The nature of the geometric algebra code generation enables one to easily extend the abstract product operations to any specific number field type (including Leibniz differentials with \textit{Leibniz.jl} or symbolic coefficients with \textit{Reduce.jl}), by making use of Julia's type system. Mixed tensor products with their coefficients are constructed from these operations to work with bivector elements of Lie groups \cite{hestenes}\cite{shahshahani}.

@@

The metric signature of the \verb+Basis{V,1}+ elements of a vector space \verb+V+ can be specified with the \verb+V"..."+ constructor by using \verb-+- and \verb+-+ to specify whether the \verb+Basis{V,1}+ element of the corresponding index squares to \verb`+1` or \verb`-1`.
For example, \verb`S"+++"` constructs a positive definite 3-dimensional \verb`VectorBundle`.
It is also possible to specify an arbitrary \verb`DiagonalForm` having numerical values for the basis with \verb`D"0,0,0"` or \verb`D"-1,1,1,1"`, although the $\pm$ format provides better performance.
Further development will result in more metric types.

@@

The \verb`AbstractTensors` package is intended for universal interoperability of the abstract \verb`TensorAlgebra` type system.
All \verb`TensorAlgebra{V}` subtypes have type parameter \verb`V`, used to store a \verb`VectorBundle` value obtained from \textit{DirectSum.jl}.
By itself, this package does not impose any specifications or structure on the \verb`TensorAlgebra{V}` subtypes and elements, aside from requiring $V$ to be a \verb`VectorBundle`.
This means that different packages can create tensor types having a common underlying \verb`VectorBundle` structure.

\begin{definition}
	Let $V\in\text{Vect}_{\mb k}$ be a \verb`VectorBundle` with dual space $V'$ and the basis elements $w_k:V\ra\mb K$, then for all $x\in V,c\in\mb K$ the properties $(w_i+w_j)(x) = w_i(x)+w_j(x)$ and $(cw_k)(x) = cw_k(x)$ hold.
	An element of a mixed-symmetry \verb`TensorAlgebra{V}` is a multilinear mapping that is formally constructed by taking the tensor products of linear and multilinear maps,
	$(\bigotimes_k \omega_k)(v_1,\dots,v_{\sum_k p_k}) = \prod_k \omega_k(v_1,\dots,v_{p_k})$.
\end{definition}
\begin{definition}[Mixed-symmetry basis]
	Combining the linear basis generating elements with each other using the multilinear tensor product yields a graded (decomposable) tensor \verb`Basis` $\langle w_{p_1}\otimes\dots\otimes w_{p_k}\rangle_k$, where \verb`grade` $k$ is determined by the number of $w_i$ basis elements in its tensor product decomposition.
	The algebra partitions into symmetric and anti-symmetric tensor equivalence classes.
	For any pair, %of tensors, either
	\begin{align*}
		&\us{\text{anti-symmetric}}{\omega\otimes\eta = -\eta\otimes\omega} & \text{or} &  &\us{\text{symmetric}}{\omega\otimes\eta = \eta\otimes\omega}.
	\end{align*}
	Typically the $k$ in a product $\plr{\partial_{p_1}\otimes\cdots\otimes\partial_{p_k}}^{(k)}$ is referred to as the \verb`order` of the element if it is fully symmetric, which is overall tracked separately from the \verb`grade` such that $\partial_k\gen{w_j}_r = \gen{\partial_kw_j}_r$ and $(\partial_k)^{(r)}\omega_j = (\partial_kw_j)^{(r)}$.
	Hence, there is a partitioning into \verb`even` grade components $\omega_+$ and \verb`odd` grade components $\omega_-$ such that $\omega_++\omega_-=\omega$.
\end{definition}
\begin{remark}
	Observe that the anti-symmetric property implies that $\omega\otimes\omega=0$, while the symmetric property neither implies nor denies such a property.
	Grassmann remarked \cite{grassmann-2} in 1862 that the symmetric algebra of functions is by far more complicated than his anti-symmetric exterior algebra.
	The first part of the book focused on anti-symmetric exterior algebra, while the more complex symmetric function algebra of Leibniz was subject of the second multivariable part of the book.
	Elements $\omega_k$ in the space $\Lambda V$ of anti-symmetric algebra are often studied as unit quantum state vectors in a unitary probability space, where $\sum_k\omega_k\neq\bigotimes_k\omega_k$ is entanglement.
\end{remark}
\begin{definition}
	The Grassmann anti-symmetric exterior basis is denoted by $v_{i_1\dots i_g}\in\Lambda_gV$ with its dual $w^{i_1\cdots i_g}\in\Lambda^gV$, while the Leibniz symmetric basis will be $\partial_{i_1}^{\mu_1}\dots\partial_{i_g}^{\mu_g}\in L_gV$ with $\epsilon_{i_1}^{\mu_1}\dots\epsilon_{i_g}^{\mu_g}\in L^gV$ dual elements.
\end{definition}
Higher-order composite tensor elements will be denoted by an oriented-multi-set $X$ %\in\text{OMSet}$
such that $w_X = \bigotimes_k w_{i_k}^{\otimes\mu_k}$ with $X = \plr{(i_1,\mu_1),\dots,(i_g,\mu_g)}$ and $|X|=\sum_k\mu_k$ is \verb`grade`,$\,$ \verb`order`.
%There are two orientations and higher multiplicities result in zero for anti-symmetric tensors denoted by indices $\Lambda X\subseteq\Lambda V$, so the only interesting multiplicity is $\mu_k\equiv 1$.
Anti-symmetric ndices $\Lambda X\subseteq\Lambda V$ have two orientations and higher multiplicities of them result in zero values, so the only interesting multiplicity is $\mu_k\equiv 1$.
Symmetric tensors have an ambiguous multiplicity of nilpotence; decide that $\epsilon_k^{\mu+1}=0$, so $\mu_k\leq\mu$ can be non-trivial, negative, or unbounded.

The Grassmann \verb`Basis` elements $v_k\in\Lambda_1V$ and $w^k\in\Lambda^1V$ are linearly independent vector and covector elements of $V$, while the Leibniz \verb`Operator` elements $\partial_k\in L_1V$ are partial tangent derivations and $\epsilon_k(x)\in L^1V$ are dependent functions of the \verb`tangent` manifold. 
Higher \verb`grade` elements of $\Lambda V$ correspond to \verb`SubManifold` subspaces, while higher \verb`order` function elements of $LV$ become homogenous polynomials and Taylor series.

@@

\begin{definition}[Poincare-Hodge dual complement]
	Let $\star\gen{\omega}_p = \gen{\omega}_p\ast I = \gen{\tilde\omega}_p\ominus I$, %= (-1)^{\frac{p(p+1)}2+\us k\sum i_k}\det\mat{ g_{i_ki_k}}\bigwedge_{m\in J(\omega)} w_m
	 then $\star : \Lambda^pV\ra\Lambda^{n-p}V$.
\end{definition}
\begin{remark}
	While $\star\omega$ is \verb`complementright` of $\omega$, the \verb`complementleft` would be $I\ast'\omega$. The $\star$ symbol was added to the Julia language as unary operator for ease of use with \verb`Grassmann` on Julia's v1.2 release.
\end{remark}
\begin{lstlisting}[language = Julia]
using Grassmann, Compose
x = Grassmann.Algebra(ℝ^7).v123
Grassmann.graph(x+!x)
draw(PDF("simplex.pdf",16cm,16cm),x+!x)
\end{lstlisting}
\begin{figure}[ht]
\centerline{\includegraphics[width=0.42\textwidth]{triangle-tetrahedron.png}}
\caption*{Triangle with its tetrahedron complement $v_{123} + \star v_{123}$ in $\mb R^7$}
\end{figure}
John Browne has discussed Grassmann duality principle in book \cite{browne}, stating that every theorem (involving either of the exterior and regressive products) can be translated into its dual theorem by replacing the $\wedge$ and $\vee$ operations and applying \textit{Poincare duality} (homology).
First applying this Grassmann duality principle to the $\wedge$ product alone, let $\set{\omega_k}_k\in\Lambda^{p_k}V, P=\sum_kp_k$, then it is possible to obtain the co-product
$\bigvee :\Lambda^{p_1}V_1\times\dots\times\Lambda^{p_g}V_g \ra \Lambda^{P-(g-1)\#V}\bigcup_k V_k$.
Grassmann's original notation implicitly combined $\wedge,\vee,\star$.
The join $\wedge$ product is analogous to union $\cup$, the meet $\vee$ product is analogous to intersection $\cap$, and the orthogonal complement $\star\mapsto^\perp$ is negation.
Together, $(\wedge,\vee,\star)$ yield an orthocomplementary propositional lattice (quantum logic):
\begin{align*}
	(\star\bigvee_k &\omega_k)(v_1,\dots,v_P) = (\bigwedge_k\star\omega_k)(v_1,\dots,v_P) \quad \textit{DeMorgan's Law},
\end{align*}
where DeMorgan's law is used to derive tensor contractions.
\begin{definition}
	Skew left $\lrcorner$ and right $\llcorner$ contractions are symmetrically defined
	$ \gen{\omega}_r\cdot\gen{\eta}_s = \begin{cases} \omega\llcorner\eta=\omega\vee\star\eta & r\geq s \\ \omega\lrcorner\eta=\eta\vee\star\omega & r\leq s \end{cases} $.
	Note for $\omega,\eta$ of equal grade, $\omega\circledast\eta = \omega\odot\eta = \omega\cdot\eta = \omega\llcorner\eta = \omega\lrcorner\eta$ are all symmetric operations. In Julia, $\lrcorner$ is $<$ and $\llcorner$ is $>$.
\end{definition}

@@

	Then  substitute this into $\int_M \omega\wedge(-1)^{mk+m+1}\star\star d\star\eta = (-1)^{km+m+1}(-1)^{(m-k+1)(k-1)}\int_M\omega\wedge d\star\eta$,
	with identity $(-1)^{km+m+1}(-1)^{(m-k+1)(k-1)}=(-1)^k$ and
	$ (-1)^k\int_M\omega\wedge d\star\eta = \int_M d(\omega\wedge\star\eta) - (-1)^{k-1}\omega\wedge d\star\eta = \int_M d\omega\wedge\star\eta$.
	Stokes identity can be proved by relying on a variant of the \textit{common factor theorem} by Browne \cite{browne}.
\end{proof}
\begin{theorem}[Clifford-Dirac-Laplacian]
	The Dirac operator \cite{garling} is $ \Delta^\frac12\omega = \pm\nabla\ominus\omega = \pm\nabla\wedge\omega \pm \nabla\cdot\omega  = \pm d\omega\pm\partial\omega$.
	\begin{align*}
		\Delta\omega &= \nabla\wedge(\omega\cdot\nabla) + (\nabla\wedge\omega)\cdot\nabla) = \pm(\pm\omega\ominus\nabla)\ominus\nabla).
	\end{align*}
	Elements $\omega$ are \textit{harmonic} if $\Delta\omega = 0$ and both \textit{exact} $d\omega=0$ and \textit{coexact} $\delta\omega=0$, such that $\mc H^p M = \setc{\Delta\omega = 0}{\omega\in \Omega^pM}$.
	Hodge \cite{ivancevic}:
	$\Omega^pM=\mc H^pM\oplus\im{d\Omega^{p-1}M}\oplus\im{\partial\Omega^{p+1}M}$.
	Note: $\nabla\omega=-\omega\nabla, \nabla^2\omega=\omega\nabla^2$ for higher-order tensor fields!
\end{theorem}

\begin{lstlisting}[language = Julia]
julia> using Reduce, Grassmann; @basis tangent(ℝ^2,3,2);

@@

julia> x^8
x ^ 8 + (8 * x ^ 7 + (4 * (2x + 7) * x ^ 6 + (8 * (x ^ 2 + 7x + 7) * x ^ 5)∂₁)∂₁)∂₁
\end{lstlisting}

@@

\begin{example}[\textit{using Leibniz $\bigoplus\,$Grassmann}]
	\textbf{julia>} S"$\infty\emptyset\text{+++"}(\nabla)$\verb`^`$2 \,\,  \mapsto\, \, \Delta = (-2\partial_{\infty\emptyset} + \partial_1^2 + \partial_2^2 + \partial_3^2)\vec v $
\end{example}
For the null-basis, complement operations are different:
\begin{align*}
	\star v_\infty &= \star(v_++v_-) = (v_- + v_+)v_{1...n} = v_{\infty1...n} \\
 	\star 2v_\emptyset &= \star(v_--v_+) = (v_+ - v_-)v_{1...n} = -2v_{\emptyset1...n}
\end{align*}
The Hodge complement satisfies $\gen{\omega\ast\omega}I=\omega\wedge\star\omega$. This property is naturally a result of using the geometric product in the definition.
An additional metric independent version of the complement operation is available with the \verb`!` operator,
\begin{align*}
	!v_\infty &= !(v_++v_-) = (v_- - v_+)v_{1...n} = 2v_{\emptyset1...n} \\
 	!2v_\emptyset &= !(v_--v_+) = (v_+ + v_-)v_{1...n} = -v_{\infty1...n}
\end{align*}
That variation of complement satisfies $\lambda I = \omega\,\wedge\,!\omega$ instead.

\begin{theorem}[Leibniz-Taylor series]
	$\partial_X=\bigominus_k\partial_k^{\mu_k}$ is defined so that $|X|=\sum_k\mu_k$, then $e^{\partial\epsilon}\omega(x)$ is
	\begin{align*}
		e^{\partial\epsilon}\omega(x) =
		\sum_{j=0}^\mu \frac{(\partial\epsilon)^{\ominus j}}{j!}\omega(x)
		= \sum_{j=0}^\mu\sum_{|X|=j} \bigominus_k \frac{(\partial_{k}\epsilon_k(x))^{\mu_{k}}}{\mu_k!}\omega(x).
		%+ (\mu+1)\sum_{|X|=\mu+1}\int_0^1(1-t)^\mu\bigominus_k\frac{(\partial_k\epsilon_k(x))^{\mu_k}}{\mu_k!}\omega(x+t\epsilon)\,dt.
	\end{align*}
\end{theorem}
The multivariate \textit{chain rule} is encoded into the geometric algebraic product when using mixed-symmetry.

In the following examples, different possible discrete bivector topologies in a projective Riemann sphere setting are examined. 
The figure below is based on the product topology of two rotation bivectors. When the standard $\mb R^4$ basis is used with projective geometric algebra, the one parameter Lie group can be visualized in the form of a torus in $\mb R^3$. When the fourth $v_\infty$ basis direction is rotated into the Minkowski plane, the double rotation becomes a helix with translational single rotation.

\begin{lstlisting}[language = Julia]
using Grassmann, Makie; @basis S"∞+++"
f(t) = (↓(exp(π*t*((3/7)*v12+v∞3))>>>↑(v1+v2+v3)))
lines(points(f,V(2,3,4)))
\end{lstlisting}
\begin{figure}[ht]
	\centering
	\begin{subfigure}[b]{0.3\textwidth}
		\includegraphics[width=\textwidth]{torus.png}
		\caption{Projective double rotation orbit}
		%\label{fig:sample_figure}
	\end{subfigure}
	~
	\begin{subfigure}[b]{0.15\textwidth}
		\includegraphics[width=\textwidth]{helix.png}
		\caption{Period translation}
		%\label{fig:sample_figure}
	\end{subfigure}
\end{figure}

\begin{figure}[t]
	\centering
	\caption{Different variations of bivectors in $\mb R^4$ discrete topology.}
	\begin{subfigure}[b]{0.14\textwidth}
		\includegraphics[width=\textwidth]{product.png}
		\caption{v_{12}+v_{34}}
		%\label{fig:sample_figure}
	\end{subfigure}
	~
	\begin{subfigure}[b]{0.14\textwidth}
		\includegraphics[width=\textwidth]{strange.png}
		\caption{v_{14}+v_{24}+v_{34}}
		%\label{fig:sample_figure}
	\end{subfigure}
	~
	\begin{subfigure}[b]{0.14\textwidth}
		\includegraphics[width=\textwidth]{toroid-modulation.png}
		\caption{v_{124}+v_{34}}
		%\label{fig:sample_figure}
	\end{subfigure}
\end{figure}

\begin{figure}[t]
\centerline{\includegraphics[width=0.45\textwidth]{orbit-3.png}}
%\caption*{$\downarrow(e^{t(v_{12}+v_\infty(sin(3t)3v_1+cos(2t)7v_2-sin(5t)4v_3)/2)}\obackslash\uparrow(v_1+v_2-v_3))$}
\caption{Modulated bivector group on Riemann sphere S"∞+++"}
\end{figure}

>>>>

The nature of the geometric algebra code generation enables one to easily extend the abstract product operations to any specific number field type (including differential operators with \textit{Leibniz.jl} or symbolic coefficients with \textit{Reduce.jl}), by making use of Julia's type system. Mixed tensor products with their coefficients are constructed from these operations to work with bivector elements of Lie groups \cite{hestenes}\cite{shahshahani}.

@@

The metric signature of the \verb+Basis{V,1}+ elements of a vector space \verb+V+ can be specified with the \verb+V"..."+ constructor by using \verb-+- and \verb+-+ to specify whether the \verb+Basis{V,1}+ element of the corresponding index squares to \verb`+1` or \verb`-1`.
For example, \verb`S"+++"` constructs a positive definite 3-dimensional \verb`VectorBundle`.
It is also possible to specify an arbitrary \verb`DiagonalForm` having numerical values for the basis with degenracy \verb`D"1,1,1,0"`, although the $\pm$ format has a more compact representation.
Further development will result in more metric types.

@@

The \verb`AbstractTensors` package is intended for universal interoperability of the abstract \verb`TensorAlgebra` type system.
All \verb`TensorAlgebra{V}` subtypes have type parameter \verb`V`, used to store a \verb`VectorBundle` value obtained from \textit{DirectSum.jl}.
By itself, this package does not impose any specifications or structure on the \verb`TensorAlgebra{V}` subtypes and elements, aside from requiring $V$ to be a \verb`VectorBundle`.
Hence all tensor types share a common underlying \verb`VectorBundle` structure.
The macro \verb`@basis V` declares a local basis in Julia.

\begin{definition}
	Let $V\in\text{Vect}_{\mb k}$ be a \verb`VectorBundle` with dual space $V'$ and the basis elements $w_k:V\ra\mb K$, then for all $x\in V,c\in\mb K$ the properties $(w_i+w_j)(x) = w_i(x)+w_j(x)$ and $(cw_k)(x) = cw_k(x)$ hold.
	An element of a mixed-symmetry \verb`TensorAlgebra{V}` is a multilinear mapping that is formally constructed by taking the tensor products of linear and multilinear maps,
	$(\bigotimes_k \omega_k)(v_1,\dots,v_{\sum_k p_k}) = \prod_k \omega_k(v_1,\dots,v_{p_k})$.
\end{definition}
\begin{definition}[Mixed-symmetry basis]
	Combining the linear basis generating elements with each other using the multilinear tensor product yields a graded (decomposable) tensor \verb`Basis` $\langle w_{p_1}\otimes\dots\otimes w_{p_k}\rangle_k$, where \verb`grade` $k$ is determined by the number of $w_i$ basis elements in its tensor product decomposition.
	The algebra partitions into symmetric and anti-symmetric tensor equivalence classes.
	For any pair, %of tensors, either
	\begin{align*}
		&\us{\text{anti-symmetric}}{\omega\otimes\eta = -\eta\otimes\omega} & \text{or} &  &\us{\text{symmetric}}{\omega\otimes\eta = \eta\otimes\omega}.
	\end{align*}
	Typically the $k$ in a product $\plr{\partial_{p_1}\otimes\cdots\otimes\partial_{p_k}}^{(k)}$ is referred to as the \verb`order` of the element if it is fully symmetric, which is overall tracked separately from the \verb`grade` such that $\partial_k\gen{w_j}_r = \gen{\partial_kw_j}_r$ and $(\partial_k)^{(r)}\omega_j = (\partial_kw_j)^{(r)}$.
	Hence, there is a partitioning into \verb`even` grade components $\omega_+$ and \verb`odd` grade components $\omega_-$ such that $\omega_++\omega_-=\omega$.
\end{definition}
\begin{remark}
	Observe that the anti-symmetric property implies that $\omega\otimes\omega=0$, while the symmetric property neither implies nor denies such a property.
	Grassmann remarked \cite{grassmann-2} in 1862 that the symmetric algebra of functions is by far more complicated than his anti-symmetric exterior algebra.
	The first part of the book focused on anti-symmetric exterior algebra, while the more complex symmetric function algebra of Leibniz was subject of the second multivariable part of the book.
	Elements $\omega_k$ in the space $\Lambda V$ of anti-symmetric algebra are often studied as unit quantum state vectors in a unitary probability space, where $\sum_k\omega_k\neq\bigotimes_k\omega_k$ is entanglement.
\end{remark}
\begin{definition}
	The Grassmann anti-symmetric exterior basis is denoted by $v_{i_1\dots i_g}\in\Lambda_gV$ with its dual $w^{i_1\cdots i_g}\in\Lambda^gV$, while the Leibniz symmetric basis will be $\partial_{i_1}^{\mu_1}\dots\partial_{i_g}^{\mu_g}\in L_gV$ with $\epsilon_{i_1}^{\mu_1}\dots\epsilon_{i_g}^{\mu_g}\in L^gV$ dual elements. Let $\Lambda V = \bigoplus \Lambda^g V$.
\end{definition}
A higher-order tensor element is an oriented-multi-set $X$ %\in\text{OMSet}$
such that $w_X = \bigotimes_k w_{i_k}^{\otimes\mu_k}$ with $X = \plr{(i_1,\mu_1),\dots,(i_g,\mu_g)}$ and $|X|=\sum_k\mu_k$ is \verb`grade`,$\,$ \verb`order`.
%There are two orientations and higher multiplicities result in zero for anti-symmetric tensors denoted by indices $\Lambda X\subseteq\Lambda V$, so the only interesting multiplicity is $\mu_k\equiv 1$.
Anti-symmetric indices $\Lambda X\subseteq\Lambda V$ have two orientations and higher multiplicities are degenerate, hence the only relevant multiplicity is $\mu_k\equiv 1$.
%Symmetric tensors have an ambiguous multiplicity of nilpotence; decide that $\epsilon_k^{\mu+1}=0$, so $\mu_k\leq\mu$ can be non-trivial, negative, or unbounded.
The Leibniz-Taylor algebra \cite{taylor-algebra} is a quotient polynomial ring $LV\cong R[x_1,\dots,x_n]/\{\prod_{k=1}^{\mu+1} x_{p_k}\}$, so that $\epsilon_k^{\mu+1}=0$. % is $\mu$ truncated % (e.g. Jacobian and Hessian).

The Grassmann \verb`Basis` elements $v_k\in\Lambda_1V$ and $w^k\in\Lambda^1V$ are linearly independent vector and covector elements of $V$, while the Leibniz \verb`Operator` elements $\partial_k\in L_1V$ are partial tangent derivations and $\epsilon_k(x)\in L^1V$ are dependent functions of the \verb`tangent` manifold. 
Higher \verb`grade` elements of $\Lambda V$ correspond to \verb`SubManifold` spaces, while higher \verb`order` function elements of $LV$ become homogenous polynomials and Taylor series.

@@

\begin{definition}[Poincare-Hodge dual complement]
	Let $\star\gen{\omega}_p = \gen{\omega}_p\ast I = \gen{\tilde\omega}_p\ominus I$, %= (-1)^{\frac{p(p+1)}2+\us k\sum i_k}\det\mat{ g_{i_ki_k}}\bigwedge_{m\in J(\omega)} w_m
	 then $\star : \Lambda^pV\ra\Lambda^{n-p}V$.
\end{definition}
\begin{remark}
	While $\star\omega$ is \verb`complementright` of $\omega$, the \verb`complementleft` would be $I\ast'\omega$. The $\star$ symbol was added to the Julia language as unary operator for ease of use with \verb`Grassmann` on Julia's v1.2 release.
\end{remark}
\begin{lstlisting}[language = Julia]
using Grassmann, Compose
x = Grassmann.Algebra(ℝ^7).v123
Grassmann.graph(x+!x)
draw(PDF("simplex.pdf",16cm,16cm),x+!x)
\end{lstlisting}
\begin{figure}[ht]
\centerline{\includegraphics[width=0.42\textwidth]{img/triangle-tetrahedron.png}}
\caption*{Triangle with its tetrahedron complement $v_{123} + \star v_{123}$ in $\mb R^7$}
\end{figure}
John Browne has discussed Grassmann duality principle in book \cite{browne}, stating that every theorem (involving either of the exterior and regressive products) can be translated into its dual theorem by replacing the $\wedge$ and $\vee$ operations and applying \textit{Poincare duality} (homology).
First applying this Grassmann duality principle to the $\wedge$ product alone, let $\set{\omega_k}_k\in\Lambda^{p_k}V, P=\sum_kp_k$, then it is possible to obtain the co-product
$\bigvee :\Lambda^{p_1}V_1\times\dots\times\Lambda^{p_g}V_g \ra \Lambda^{P-(g-1)\#V}\bigcup_k V_k$.
Grassmann's original notation implicitly combined $\wedge,\vee,\star$.
The join $\wedge$ product is analogous to union $\cup$, the meet $\vee$ product is analogous to intersection $\cap$, and the orthogonal complement $\star\mapsto^\perp$ is negation.
Together, $(\wedge,\vee,\star)$ yield an orthocomplementary propositional lattice (quantum logic):
\begin{align*}
	(\star\bigvee_k &\omega_k)(v_1,\dots,v_P) = (\bigwedge_k\star\omega_k)(v_1,\dots,v_P) \quad \textit{DeMorgan's Law},
\end{align*}
where DeMorgan's law is used to derive tensor contractions.
\begin{definition}
	Skew left $\lrcorner$ and right $\llcorner$ contractions are symmetrically defined
	$ \gen{\omega}_r\cdot\gen{\eta}_s = \begin{cases} \omega\llcorner\eta=\omega\vee\star\eta & r\geq s \\ \omega\lrcorner\eta=\eta\vee\star\omega & r\leq s \end{cases} $.
	Note for $\omega,\eta$ of equal grade, $\omega\circledast\eta = \omega\odot\eta = \omega\cdot\eta = \omega\llcorner\eta = \omega\lrcorner\eta$ are all symmetric operations. In Julia, $\lrcorner$ is $<$ and $\llcorner$ is $>$.
\end{definition}

@@

	Then  substitute this into $\int_M \omega\wedge(-1)^{mk+m+1}\star\star d\star\eta = (-1)^{km+m+1}(-1)^{(m-k+1)(k-1)}\int_M\omega\wedge d\star\eta$,
	with identity $(-1)^{km+m+1}(-1)^{(m-k+1)(k-1)}=(-1)^k$ and
	$ (-1)^k\int_M\omega\wedge d\star\eta = \int_M d(\omega\wedge\star\eta) - (-1)^{k-1}\omega\wedge d\star\eta = \int_M d\omega\wedge\star\eta$.
	Stokes identity can be proved by relying on a variant of the \textit{common factor theorem} by Browne \cite{browne}.
\end{proof}
\begin{theorem}[Clifford-Dirac-Laplacian]
	The Dirac operator \cite{garling} is $ (\nabla^2)^\frac12\omega = \pm\nabla\ominus\omega = \pm\nabla\wedge\omega \pm \nabla\cdot\omega  = \pm d\omega\pm\partial\omega$.
	\begin{align*}
		\nabla^2\omega &= \nabla\wedge(\omega\cdot\nabla) + (\nabla\wedge\omega)\cdot\nabla) = \mp(\mp\omega\ominus\nabla)\ominus\nabla).
	\end{align*}
	Elements $\omega$ are \textit{harmonic} if $\nabla\omega = 0$ and both \textit{exact} $d\omega=0$ and \textit{coexact} $\delta\omega=0$, such that $\mc H^p M = \setc{\nabla\omega = 0}{\omega\in \Omega^pM}$.
	Hodge \cite{ivancevic}:
	$\Omega^pM=\mc H^pM\oplus\im{d\Omega^{p-1}M}\oplus\im{\partial\Omega^{p+1}M}$.
	Note: $\nabla\omega=-\omega\nabla, \nabla^2\omega=\omega\nabla^2$ for higher-order tensor fields!
\end{theorem}

\iffalse
\begin{lstlisting}[language = Julia]
julia> using Reduce, Grassmann; @basis tangent(ℝ^2,3,2);

@@

julia> x^8
x ^ 8 + (8 * x ^ 7 + (4 * (2x + 7) * x ^ 6 + (8 * (x ^ 2 + 7x + 7) * x ^ 5)∂₁)∂₁)∂₁
\end{lstlisting}
\fi

@@

For the null-basis, complement operations are different:
\begin{align*}
	\star v_\infty &= \star(v_++v_-) = (v_- + v_+)v_{1...n} = v_{\infty1...n} \\
 	\star 2v_\emptyset &= \star(v_--v_+) = (v_+ - v_-)v_{1...n} = -2v_{\emptyset1...n}
\end{align*}
The Hodge complement satisfies $\gen{\omega\ast\omega}I=\omega\wedge\star\omega$. This property is naturally a result of using the geometric product in the definition.
An additional metric independent version of the complement operation is available with the \verb`!` operator,
\begin{align*}
	!v_\infty &= !(v_++v_-) = (v_- - v_+)v_{1...n} = 2v_{\emptyset1...n} \\
 	!2v_\emptyset &= !(v_--v_+) = (v_+ + v_-)v_{1...n} = -v_{\infty1...n}
\end{align*}
That variation of complement satisfies $\lambda I = \omega\,\wedge\,!\omega$ instead.
\begin{example}%[\textit{using Leibniz $\bigoplus\,$Grassmann}]
	S"$\infty\emptyset\text{+++"}(\nabla$\verb`^`$2) \,\,  \mapsto\, \, -2\partial_{\infty\emptyset} + \partial_1^2 + \partial_2^2 + \partial_3^2 $
\end{example}
Let $\nabla\in\Lambda^1V$, then $\omega = (\nabla\bs\nabla)\ominus\omega = \nabla\bs(d\omega + \partial\omega)$ where $\nabla\parallel\partial\omega$ and $\nabla\perp d\omega$.
Let's reflect across the hyperplane $\star\nabla$,
\begin{align*}
	\nabla\bs (d\omega-\partial\omega) &= \nabla\bs(d\omega-\partial\omega)\ominus(\nabla\bs\nabla) \\
									   &= -\nabla^2\bs(d\omega+\partial\omega)\ominus\nabla = -\nabla\bs\omega\ominus\nabla. %= \omega\oslash\nabla
\end{align*}
Hence, reflection by hyperplane $\star\nabla$ has isometry $\omega\oslash\nabla$ which for $\nabla = v_j$ is the map $\mb R^n \ra \mb R_1\times\cdots\times\conj{\mb R}_j\cdots\times\mb R_n$.

\begin{theorem}[Cartan-Dieudonne]
	Every isometry of $V\ra V$ is the composite of at most $k$ reflections across non-singular hyperplanes. Hence there exist vectors $\nabla_j$ such that
	$$ (((\omega\oslash\nabla_1)\oslash\nabla_2)\oslash\cdots)\oslash\nabla_k = \omega\oslash(\nabla_1\ominus\nabla_2\ominus\dots\ominus\nabla_k) $$
	for any isometry element of the orthogonal group $O(p,q)$.
\end{theorem}
Note that elements under transformations of this group preserve inner product relations.
The even grade operators make up the rotational group, where each bivector isometry is a composition of two reflections \cite{artin} \cite{doran-hestenes-sommen-acker}.

Consider the differential equation $ \partial_i\epsilon_j = \epsilon_j\oslash\omega$ with the solution $\epsilon_j(x) = \epsilon_j(0)\oslash e^{x_i\omega} $ where $\theta =2 x_i$ is the parameter of the Lie group. Then for a normalized $\omega$,
$$ e^{\theta\omega} = \sum_k \frac{(\theta\omega)^{\ominus k}}{k!} = \begin{cases} \cosh\theta+\omega\sinh\theta, & \text{if } \omega^2 = 1, \\ \cos\theta + \omega\sin\theta, & \text{if } \omega^2=-1, \\ 1+\theta\omega, & \text{if } \omega^2=0. \end{cases} $$
Note that $\nabla\oslash e^{\theta\omega/2} = \nabla \ominus e^{\theta\omega}$ is a double covering when using the complex numbers in the Euclidean plane.
\begin{theorem}[Leibniz-Taylor series]
	$\partial_X=\bigominus_k\partial_k^{\mu_k}$ is defined so that $|X|=\sum_k\mu_k$, then $e^{\partial\epsilon}\omega(x)$ is
	\begin{align*}
		e^{\partial\epsilon}\omega(x) =
		\sum_{j=0}^\mu \frac{(\partial\epsilon)^{\ominus j}}{j!}\omega(x)
		= \sum_{j=0}^\mu\sum_{|X|=j} \bigominus_k \frac{(\partial_{k}\epsilon_k(x))^{\mu_{k}}}{\mu_k!}\omega(x).
		%+ (\mu+1)\sum_{|X|=\mu+1}\int_0^1(1-t)^\mu\bigominus_k\frac{(\partial_k\epsilon_k(x))^{\mu_k}}{\mu_k!}\omega(x+t\epsilon)\,dt.
	\end{align*}
\end{theorem}
The multivariate \textit{product rule} is encoded into the geometric algebraic product when using mixed-symmetry.

\begin{lstlisting}[language = Julia]
using Grassmann, Makie
basis"2" # Euclidean
streamplot(vectorfield(v1*exp(π*v12/2)),-1.5..1.5,-1.5..1.5)
streamplot(vectorfield(exp((π/2)*v12/2)),-1.5..1.5,-1.5..1.5)
streamplot(vectorfield(exp((π/4)*v12/2)),-1.5..1.5,-1.5..1.5)
streamplot(vectorfield(v1*exp((π/4)*v12/2)),-1.5..1.5,-1.5..1.5)
@basis S"+-" # Hyperbolic
streamplot(vectorfield(exp((π/8)*v12/2)),-1.5..1.5,-1.5..1.5)
streamplot(vectorfield(v1*exp((π/4)*v12/2)),-1.5..1.5,-1.5..1.5)
\end{lstlisting}
\begin{figure}[ht]
	\centering
	%\caption{Euclidean vector fields based on exponential operator:}
	\begin{subfigure}[b]{0.23\textwidth}
		\includegraphics[width=\textwidth]{img/plane-1.png}
		\caption{$x\oslash e^{\pi v_{12}/2}$, $\mb R^2$}
		%\label{fig:sample_figure}
	\end{subfigure}
	~
	\begin{subfigure}[b]{0.23\textwidth}
		\includegraphics[width=\textwidth]{img/plane-2.png}
		\caption{$ x\oslash e^{\frac\pi2 v_{12}/2}$, $\mb R^2$}
		%\label{fig:sample_figure}
	\end{subfigure}

	\begin{subfigure}[b]{0.23\textwidth}
		\includegraphics[width=\textwidth]{img/plane-3.png}
		\caption{$x\oslash e^{\frac\pi4 v_{12}/2}$, $\mb R^2$}
		%\label{fig:sample_figure}
	\end{subfigure}
	~
	\begin{subfigure}[b]{0.23\textwidth}
		\includegraphics[width=\textwidth]{img/plane-4.png}
		\caption{$x\oslash(v_1\ominus e^{\frac\pi4 v_{12}/2})$, $\conj{\mb R}\oplus\mb R$}
		%\label{fig:sample_figure}
	\end{subfigure}

	\begin{subfigure}[b]{0.23\textwidth}
		\includegraphics[width=\textwidth]{img/plane-5.png}
		\caption{$x\oslash e^{\frac\pi8 v_{12}/2}$, $\mb R\oplus\mb R'$}
		%\label{fig:sample_figure}
	\end{subfigure}
	~
	\begin{subfigure}[b]{0.23\textwidth}
		\includegraphics[width=\textwidth]{img/plane-6.png}
		\caption{$x\oslash(v_1\ominus e^{\frac\pi4 v_{12}/2})$, $\conj{\mb R}\oplus\mb R'$}
		%\label{fig:sample_figure}
	\end{subfigure}
\end{figure}
